Spin canonical rings of log stacky curves

### 2015-07-07 curves-write-up/spin_cring.tex
flip order of examples in curves, needs details
minor example edits

@@

By the Generalized Max Noether Theorem for genus 0 curves, (see Voight
and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
\begin{align}
\label{eqn:noether-377}
	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan' \rfloor)
\end{align}

@@

\noindent
are surjective. This reduces the problem to checking generation
in the degrees of the exceptions $d \in \{8, 12, 21\}$.
Checking the remaining cases via pole degrees shows that
these degrees are also generated in lower degrees,
so $R'$ is generated in degrees $\{3, 5, 7, 7\}$.

@@

Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order. The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.

We next check $(\sx', \halfcan', \{1,2\})$ is admissible. We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction. Hence, \ref{custom:Ad-i} holds. We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric. Here, by construction
$$
\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
	0 &\text{ if }z \in \{u, y_3\}\\
	\frac{1}{4} &\text{ if }z = y_4
\end{cases}.$$
Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
\end{example}

>>>>

Then, there exist constants $\alpha, \beta, \gamma \in k$ so that 
$R_{\halfcan'} \cong k[u, x, y_3, y_4]/(xy_3- \alpha uy_4, y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic: We may first use Riemann--Roch to compute the dimensions of $(R_{\halfcan'})_n$ over $k$, then verify that these generators and relations produce the correct number of independent functions via an analysis of zero and pole order. The details are omitted as it is analogous to Example ~\ref{eg:base-0-377}.
\todo{fill in details here.
Use Generalized Max Noether Theorem for genus 1 curves (see Voight and Zureick-Brown \cite[Lemma 3.1.3]{vzb:stacky}.}

We next check $(\sx', \halfcan', \{1,2\})$ is admissible. We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction. Hence, \ref{custom:Ad-i} holds. We next check \ref{custom:Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric. Here, by construction
\[
\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
	0 &\text{ if }z \in \{u, y_3\}\\
	\frac{1}{4} &\text{ if }z = y_4
\end{cases}.
\]
Since $0, \frac{1}{4} < \frac{1}{3}$, \ref{custom:Ad-ii} holds.
Finally, to check \ref{custom:Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = (2 g - 1) + 0$.
\end{example}

@@

By the Generalized Max Noether Theorem for genus 0 curves (see Voight
and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}),
\begin{align}
\label{eqn:noether-377}
	H^0 (\sx', \lfloor 21 \cdot \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan' \rfloor)
\end{align}

@@

\noindent
are surjective. This reduces the problem to checking generation
in the degrees of the exceptions $d \in \{8, 12, 21\}$.
Checking these remaining cases via pole degree considerations shows
that these degrees are also generated in lower degrees. Thus, $R'$
is generated in degrees $\{3, 5, 7, 7\}$.

@@
